### 2021-07-03 docs/manuscript/manuscript.tex
Add field size experiments to methods

@@

>>>>

\subsection*{Change in morphogenetic field size}
We wanted to evaluate if the GRNs evolved in our model with a morphogenetic
field size of 30 cells could produce the desired pattern in morphogenetic fields
with a different number of cells. For this reason, we calculated the fitness of
each GRN in morphogenetic fields with 10, 20, 40, and 50 cells. In these
simulations we redefined the morphogen gradient in such a way that the initial
and final concentration were constant in all the fields (\nameref{S5_Fig}).
In order to know if topologies with the same topology had a similar fitness
in the different fields, we performed a Principal Component Analysis in
Scikit-learn~0.24.2~\cite{sklearn} using the fitness values of each GRN in
the four different fields.

@@

\paragraph*{S5 Fig.}
\label{S5_Fig}
{\bf Response of GRNs to changes in morphogenetic field size.}
(A) Morphogen gradients of fields with 10, 20, 40 and 50 cells. (B) Fitness of the
GRNs in each one of the morphogenetic fields. (C) Principal Component Analysis
of fitness by morphogenetic field size. Although principal components separate
GRNs in clusters, not all the GRNs with the same topology are located in the
same group. (D) Average fitness of GRNs evolved in different morphogenetic
field sizes.
